Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
model 2

>>>>

# ```{r}
# model_1 <- stan_glmer(
#   ChinaVirusInterest ~ Day + (Day | State),
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 5000*2, refresh = 0
# )
# ```

```{r}
model_2 <- stan_glmer(
  ChinaVirusInterest ~ (1 | Region),
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

```{r}
mcmc_trace(model_2)
mcmc_dens_overlay(model_2)
```

```{r}
# Store the chains
model_2_df <- as.array(model_2) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_2_df <- model_2_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_2_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

```{r}
head(data.frame(summary(model_2)),-2)
```
